A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
moved representativity analysis to discussion
decided to move region wise comparison to results section

- Characteristics and map of final dataset

- Absolute and relative temporal development of traits by region

>>>>

Figure \ref{development_burial_type} and \ref{development_burial_construction} show the region wise timeseries of trait occurrence. The relative proportion of each trait calculated based on ^14^C dates can be compared to the archaeological state of research:

### 2018-12-17 article/04_Discussion.Rmd
added conclusion segment
decided to move region wise comparison to results section

Figure \ref{development_burial_type} and \ref{development_burial_construction} show the region wise timeseries of trait occurrence. The figure part A with absolute numbers indicates areas and timeperiods with a lot, and others with very few points of data. For some there is not enough information to make any decision about the relative dominance and for many the general relevance and accuracy of the resulting timeseries can be questioned. There's a variety of reasons for this:

@@

- General and concluding observations

The data representativity and semantic consequences will be discussed below.

>>>>

The A sections of the figures \ref{development_burial_type} and \ref{development_burial_construction} with absolute grave numbers per region and year indicate areas and timeperiods with a lot, and others with very few points of data. For some there is not enough information to make any decision about the relative dominance and for many the general relevance and accuracy of the resulting timeseries can be questioned. There's a variety of reasons for this:

@@
